---
title: "Process Raster Tiles"
subtitle: "Mosaic and Change Resolutions"
author: "Colin Chisholm"
date: "10/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval=FALSE, ##generally processing is in script.
                      warning = FALSE,
                      message = FALSE)



library(foreach)
# devtools::install_github("ColinChisholm/pemgeneratr")
library(pemgeneratr)
library(rgdal)
library(gdalUtils)
```

## Purpose

Generally, working with lidar generated products a high resolution tileset of rasters (e.g. 1m resolution) is provided as a product.  This script takes those tiles resamples them to a desired resolution or set of resolutions and then generates a mosaic of the resulting tilesets.

1. Take the initial tileset, usually 1m, and generate a massive mosaic
2. Snap this resulting raster in or out to the nearest 100m -- this is to facilitate latter raster stacking. 
3. [Optional] Generate tiles -- which can be processed faster 
1. Takes an input raster list and outputs them to different resolutions. ... alternately just use 
2. Create a mosaic of the rasters tiles

_The continuous issue remains -- stackability of the rasters through the pem process.  Ideally, the full mosaic of the 1m raster should be generated first and the `aoi_snap()` used to trim or expand to a set number that this divisible by all of the


### Notes:

- this script assumes rasters are in a UTM based projection (i.e. in metres)
-

  ## Process tiles to alternate resolutions

  ### I/O

  _Adjust the following codeblock to your own situation._

```{r InOutSettings}
## Inputs -- create list of rasters to process
rsPath <- "/home/rstudio/data/DLL/BareEarth"

rs <- list.files(path = rsPath,
                 pattern = "tif", full.names = TRUE)

## Output -- folder to save rasters
outName <- "DLL_dtm" ## will be used as the suffix for the output mosaic
outdir <- file.path("/home/rstudio/data/DLL/BareEarth/multi_res2")

## desired output resolutions
resSet <- c(2.5, 5, 10, 25)
```

### Process the rasters

Generates the rasters in various resolutions.  _Processed in parallel_.

```{r AltRes-Rasters}
## DO NOT CHANGE THIS
cl <- parallel::makeCluster(parallel::detectCores())
doParallel::registerDoParallel(cl)

foreach(i = rs) %dopar%
  {
    r <- raster::raster(i)
    pemgeneratr::multi_res(input = r, output = outdir, resolution = resSet)
  }

parallel::stopCluster(cl)
```



### Mosaic the rasters

**`r length(resSet)`** sets of raster tiles have been generated.  This next step code clock cycles through each set to create a continuous cover mosaic.

```{r}
# 1m set:
rs <- list.files(file.path("/home/rstudio/data/DLL/BareEarth/"),
                 pattern = "tif",
                 full.names = TRUE,
                 recursive = FALSE
)

## ADD declare cores
foreach (i = resSet) %do%
  {
    i <- "1m"  ## Testing


    ## create output directory
    if(!dir.exists(file.path(outdir, "mosaics"))) {
      dir.create(file.path(outdir, "mosaics"))  }

    ## get list of files
    rs <- list.files(file.path(outdir, i),
                     pattern = "tif", full.names = TRUE)

    # 1m set: here I used this to generate a mosaic of the original 1m dataset
    # rs <- list.files(file.path("/home/rstudio/data/DLL/BareEarth/"),
    #              pattern = "tif",
    #              full.names = TRUE,
    #              recursive = FALSE
    #              )

    ## gdal mosaic fails to compile all of the tiles... if there are too many
    ## create a set of raster-sets -- with a max of 500 each
    # x <- seq_along(rs)
    # rsSet <- split(rs, ceiling(x/500))
    #
    # ## if long list, create a tmp dir, tile each set ... then mosaic those
    # if (length(rsSet) > 1) {dir.create(file.path(outdir, "mosaics", "tmp"))
    #
    #   for (j in 1:length(rsSet)) {
    #     rs <- as.character(unlist(rsSet[j]))
    #
    #     mosaicOutTmp <- file.path(outdir, "mosaics", "tmp",
    #                        paste0(outName, "_", i,"-",j, ".tif"))
    #     gdalUtils::mosaic_rasters(rs, mosaicOutTmp)
    #   }


    # }



    mosaicOut <- file.path(outdir, "mosaics",
                           paste0(outName, "_", i, ".tif"))
    gdalUtils::mosaic_rasters(rs, mosaicOut)
  }


```


